Estimating duration in the presence of misclassification

### 2023-12-21 incidence-prevalence.tex
easy edits

The \emph{No U-Turn Sampler} (NUTS)~\autocite{hoffmanNUTS} is a variant of HMC that automatically tunes the number of leapfrog steps to take in the Hamiltonian dynamics.
NUTS has been implemented in a variety of software packages making it easy to apply to arbitrary posterior distributions.
I will make use of the implementation in the package \emph{Sampling through adaptive neighborhoods} (Stan)~\autocite{Stan-2-32-2}.
Stan implements \emph{automatic differentiation}\todo{cite automatic diff} to calculate the gradient of the posterior density without any user input.
Automatic differentiation uses the chain rule to calculate the gradient of a function from its code by breaking it down into a series of elementary operations, for which the gradient is known.
For a more detailed introduction to HMC, NUTS, and Stan see \textcite[chapter 12]{gelmanBDA}.

>>>>

The \emph{No U-Turn Sampler} (NUTS)~\autocite{hoffmanNUTS} is a variant of HMC that automatically tunes the number of leapfrog steps to take in the Hamiltonian dynamics.
NUTS has been implemented in a variety of software packages making it easy to apply to arbitrary posterior distributions.
I will make use of the implementation in the package \emph{Sampling through adaptive neighborhoods} (Stan)~\autocite{Stan-2-32-2}.
Stan implements \emph{automatic differentiation} to calculate the gradient of the posterior density without any user input.
Automatic differentiation uses the chain rule to calculate the gradient of a function from its code by breaking it down into a series of elementary operations, for which the gradient is known~\autocite{autodiff}.
For a more detailed introduction to HMC, NUTS, and Stan see \textcite[chapter 12]{gelmanBDA}.

### 2023-12-21 introduction.tex
easy edits

The ATACCC data used is found in the same location.
CIS data can only be accessed by accredited researchers within the Office for National Statistic's Secure Research Service\todo{insert details of applying}.
Where possible, aggregated, non-disclosive versions of the dataset are available alongside the code.

>>>>

The ATACCC data used is found in the same location.
CIS data can only be accessed by accredited researchers within the Office for National Statistic's Secure Research Service\todo{insert details of applying to SRS}.
Where possible, aggregated, non-disclosive versions of the dataset are available alongside the code.
